AHABus \& FCORE: A Modular Bus System for High-Altitude Balloon Missions

### 2017-04-25 chapters/02-lit-review.tex
Proof read lit review

While small-budget missions are built around commercial off-the-shelf small computers, or micro-controller-based boards for their \acrlong{obc} and instruments, the resulting designs are often non-modular, combine different communications standard in order to communicate with an heterogenous set of instruments, and make use of customised, text-based telemetry formats in the United Kingdom.

@@

On other projects like Emmanuel Bonbasaro's (\cite{Bombasaro2015}) Titan-1 mission, a micro-controller boards like an ``Arduino Mega 2560 is [...] used as flight computer'', alongside multiple commercial sensors connected to the \acrshort{obc} through multiple different data buses (in this case \acrfull{i2c} and \acrfull{spi}), because of the disparate communication standards in use in affordable commercial sensors. The flight software discussed by the author is a custom-made solution developed specifically for Titan 1's architecture, which would render its re-use in a different mission complicated.

@@

When space conditions are required, or when the targeted scientific observations require longer or more global exposure times, nano-satellites have become popular over the last decade ( \cite{McDowell2017a}, \cite{McDowell2017}) as a relatively affordable – though much more costly than \acrshort{hab} missions – access to space. The most popular standard is CubeSat (\cite{Heidt2000}), based on \SI{10}{\centi\metre} cubes small and light enough to be launched as secondary payloads, and thus only require a small portion of the launch costs to be covered by nano-satellites teams.

@@

Thomas Clausen (\cite{Clausen2001}) describes in his 2001 paper the design of an internal bus for CubeSats based on the \acrshort{i2c} protocol as well. In this case too, \acrshort{i2c} was chosen for its low power consumption and I/O line usage, but also for its speed and reliance to noise, and because the addressing of payloads on the bus can be done entirely in software. T. Clausen proposes the use of a limited packet system on top of \acrshort{i2c} in order to provide stable data transfers between payloads and the \acrlong{obc}.

>>>>

While small-budget missions are built around commercial off-the-shelf small computers or micro-controller boards for their \acrlong{obc} and instruments, the resulting designs are often non-modular, combine different communications standard in order to communicate with an heterogenous set of instruments, and make use of customised, text-based telemetry formats in the United Kingdom.

@@

On other projects like Emmanuel Bonbasaro's (\cite{Bombasaro2015}) Titan-1 mission, a micro-controller board like an ``Arduino Mega 2560 is [...] used as flight computer'', alongside multiple commercial sensors connected to the \acrshort{obc} through multiple different data buses (in this case \acrfull{i2c} and \acrfull{spi}), because of the disparate communication standards in use in affordable commercial sensors. The flight software discussed by the author is a custom-made solution developed specifically for Titan 1's architecture, which would render its re-use in a different mission complicated.

@@

When space conditions are required, or when the targeted scientific observations require longer or more global exposure times than are achievable using High-Altitude Balloons, nano-satellites have become popular over the last decade ( \cite{McDowell2017a}, \cite{McDowell2017}) as a relatively affordable – though much more costly than \acrshort{hab} missions – access to space. The most popular standard is CubeSat (\cite{Heidt2000}), based on \SI{10}{\centi\metre} cubes small and light enough to be launched as secondary payloads, and thus only require a small portion of the launch costs to be covered by nano-satellites teams.

@@

Thomas Clausen (\cite{Clausen2001}) describes in his 2001 paper the design of an internal bus for CubeSats based on the \acrshort{i2c} protocol as well. In this case too, \acrshort{i2c} was chosen for its low power consumption and I/O line usage, but also for its speed and resilience to noise, and because the addressing of payloads on the bus can be done entirely in software. T. Clausen proposes the use of a limited packet system on top of \acrshort{i2c} in order to provide stable data transfers between payloads and the \acrlong{obc}.
